---
title: "Americans' Attitudes Toward The Employment of Homosexual Individuals in Colleges or Universities"
subtitle: "[one sentence of the findings from the paper]"
author: 
  - Linrong Li
thanks: "Code and data are available at: https://github.com/linforestli/homosexual_attitude.git "
date: "`r Sys.time()`"
date-format: "D MMMM YYYY"
abstract: "This study investigates the attitudes of Americans towards the employment of homosexual individuals as teachers in colleges or universities. Using data from the U.S. General Society Survey and logistic regression analysis, the study explores factors that may influence these attitudes, such as sex, region, and political beliefs. This research addresses a gap in the literature, as previous studies have mainly focused on homosexual teachers in elementary and secondary education. [One sentence about the findings that I do not know right now]"
format: 
  pdf: 
    documentclass: article
number-sections: true
bibliography: references.bib
---

```{r}
#| include: false
#| warning: false
#| message: false

library(tidyverse)
```

# Introduction

In recent years, the issue of whether sexual orientation should be a factor in determining employment eligibility has been a controversial topic in the United States, particularly in the context of hiring homosexual teachers in universities. This study aims to investigate Americans' attitudes toward allowing homosexual individuals to teach in colleges or universities, with a specific focus on the factors that may influence these attitudes. Through examining factors such as sex, the region they were located, and political beliefs, this study seeks to provide a deeper understanding of the complexity of the debate and the varying opinions on the matter.

To achieve the research objectives, a data set was first collected from the U.S. General Society Survey. Then, the data was cleaned and summarized by graphs and tables to illustrate the important features of the data. Furthermore, predicted probability models were established using logistic regression to predict the likelihood of the influence of the investigated factors on their attitudes toward allowing homosexual people to teach.

\[This will be a paragraph talking about the findings; have not finished the research so do not know the findings yet\]

Currently, most studies focused on the employment of homosexual teachers in elementary and secondary education and exploring the influence of homosexual teachers on younger children. The study addresses a significant gap in the literature on this topic, as research on Americans' attitudes toward the employment of homosexual teachers in universities remains limited. The findings of this study could potentially inform university policies and employment practices, particularly as institutions strive to create more inclusive and diverse environments.

This paper is structured as follows. @sec-data provides an overview of the data set, summarizing the key features of the data set. @sec-model details the models used in this study. @sec-results presents the results of the study, while @sec-discussion discusses the findings and their potential implications for university policies and employment practices.

# Data {#sec-data}

```{r}
#| label: fig-bills
#| fig-cap: Bills of penguins
#| echo: false
```

```{r}
#| label: fig-billssssss
#| fig-cap: More bills of penguins
#| echo: false
#| fig-width: 8
#| fig-height: 4
```

# Model {#sec-model}

$$
log({p \over 1-p}) = \beta_0 + \beta_1 \cdot x_1 
\begin{cases}
  1, & \text{if sex is female}\\
  0, & \text{otherwise}
\end{cases}
$$ {#eq-sex}

@eq-sex models the relationship between sex and the probability female would allow a homosexual individual to teach in universities or colleges.

# Results {#sec-results}

# Discussion {#sec-discussion}

## First discussion point {#sec-first-point}

## Second discussion point

## Third discussion point

## Weaknesses and next steps

\newpage

\appendix

# Appendix {.unnumbered}

# Additional details

\newpage

# References
